Hydraulic bore interaction with a column - A comparison between the solution of the shallow equation and experimental results

### 2015-03-10 doc/paper/paper.tex
Changes to abstract and title

\title{Comparison of the solution of the shallow equation with experimental}

@@

\begin{abstract}
In this paper we compare the solution of the shallow water equations with experimental results. The experiment simulates the interaction between an incident bore and a free-standing coastal structure. The shallow water equations are solved using the CLAWPACK software.
\par
Three different cases are simulated and compared. In the first case, the column is removed. 
This is a simple dambreak problem and history of wave height and velocity at where column center should be are measured and compared. 
In the second case, a square column is set and wave height at some locations ahead the column are measured and compared. 
For the third case, the square column is replaced with a cylinder with the same data measured and compared. 
The discrepancy between geoclaw simulation and experiment results are also discussed and analyzed in a deep manner.
\end{abstract}

>>>>

\title{Hydraulic bore interaction with a column - A comparison between the solution of the shallow equation and experimental results}

@@

\begin{abstract}
In this paper we compare the solution of the shallow water equations with experimental results. The experiment simulates the interaction between an incident bore and a free-standing coastal structure. The shallow water equations are solved using the GeoClaw solver of the CLAWPACK software.
\par
Three different cases are simulated and compared. In the first case a simple dam break problem is performed and evaluated.
The history of the wave height and velocity at the center location, where the column will be mounted are compared. 
In the second case, a square column is added and wave height at various locations in front of the column are measured and compared. 
For the third case, the square column is replaced by a cylinder column and the same variables are measured and compared. 
The discrepancy between the GeoClaw simulation and the experimental results are discussed and analyzed.
\end{abstract}
